---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# yelpredict

<!-- badges: start -->
<!-- badges: end -->

The goal of yelpredict is to provide a fast and accurate classification model that prdicts a Yelp review's rating based on its text. The package follows tidy principles and works with the pipe operator. The code is vectorized so can process thousands of reviews in seconds, and it was approximately 84.5% accurate on a balanced dataset of over 200,000 Yelp reviews.

## Installation

You can install the released version of yelpredict from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages("yelpredict")
```

And the development version from [GitHub](https://github.com/) with:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("chris31415926535/yelpredict")
```

## Example

This is a basic example that shows how to apply the model to three short sample interviews:

```{r example}
library(yelpredict)
library(tibble)

review_examples <- tribble(
  ~"review_text", ~"true_rating",
  "This place was awful!", "NEG",
  "The service here was great I loved it it was amazing.", "POS",
  "Meh, it was pretty good I guess but not the best.", "POS"
)

review_examples %>%
  prepare_yelp(review_text) %>%
  get_prob() %>%
  predict_rating() %>%
  knitr::kable()

```

If you have the true review ratings, the package provides the function `get_accuray()` as a convenience wrapper to `summarise()` that accepts the name of the true-rating column.

```{r cars}
review_examples %>%
  prepare_yelp(review_text) %>%
  get_prob() %>%
  predict_rating() %>%
  get_accuracy(true_rating) %>%
  knitr::kable()

```

## For more details

* [This blog post](FIXME) has more details on the motivation, methodology, and empirical results.

* I created this model as part of an MBA-level directed reading in natural language processing at the University of Ottawa's Telfer School of Management. For anyone interested [my entire lab notebook is available here, warts and all](https://chris31415926535.github.io/mba6292/). 
